---
title: "HANAMI Figure 5: complete cohort with error bars"
output: html_document
params:
  source: "results/clinical_concordance/figure5/validated_gene_star_motifs_1630_mean10.tsv"
  case_source: "data/clinical_concordance/current/figure5_cases_5.csv"
  seed_source: "results/clinical_concordance/figure5/figure5_case_seed_percentiles.csv"
  bar_alpha: 0.8
  layout_columns: 4
  output_stats: "results/clinical_concordance/figure5/figure5_complete_cohort_cluster_robust_results.csv"
  output_source: "results/clinical_concordance/figure5/figure5_plot_source.csv"
  output_case_summary: "results/clinical_concordance/figure5/figure5_case_rank_summary.csv"
  output_case_tests: "results/clinical_concordance/figure5/figure5_case_seed_tests.csv"
  output_pdf: "results/clinical_concordance/figure5/figure5.pdf"
  output_png: "results/clinical_concordance/figure5/figure5.png"
  width: 14
  height: 8
  dpi: 300
---

This document compares ten-seed motif rankings across five methods in the MS
clinical evidence cohort. Panels a-b summarize cohort performance, and panels
c-g show five representative motifs. See [README.md](README.md) for input and
execution instructions.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

input_file <- knitr::current_input(dir = TRUE)
analysis_dir <- normalizePath(dirname(input_file), winslash = "/", mustWork = TRUE)
repo_root <- normalizePath(file.path(analysis_dir, "../.."), winslash = "/", mustWork = TRUE)

resolve_repo_path <- function(value) {
  if (grepl("^([A-Za-z]:[/\\\\]|/)", value)) return(value)
  file.path(repo_root, value)
}

source_path <- resolve_repo_path(params$source)
case_source_path <- resolve_repo_path(params$case_source)
seed_source_path <- resolve_repo_path(params$seed_source)
bar_alpha <- as.numeric(params$bar_alpha)
layout_columns <- as.integer(params$layout_columns)
output_stats <- resolve_repo_path(params$output_stats)
output_source <- resolve_repo_path(params$output_source)
output_case_summary <- resolve_repo_path(params$output_case_summary)
output_case_tests <- resolve_repo_path(params$output_case_tests)
output_pdf <- resolve_repo_path(params$output_pdf)
output_png <- resolve_repo_path(params$output_png)

if (length(bar_alpha) != 1L || is.na(bar_alpha) ||
    bar_alpha <= 0 || bar_alpha > 1) {
  stop("bar_alpha must be greater than 0 and no greater than 1")
}
if (length(layout_columns) != 1L || is.na(layout_columns) ||
    layout_columns < 2L || layout_columns > 6L) {
  stop("layout_columns must be an integer from 2 to 6")
}
cohort_label <- "Complete clinical cohort"

if (!file.exists(source_path)) {
  stop("Strict-evidence motif table not found: ", source_path)
}
if (!file.exists(case_source_path)) {
  stop("Illustrative-case table not found: ", case_source_path)
}
```

## Packages and input data

```{r packages}
library(ggplot2)
library(tidyr)
library(dplyr)
library(patchwork)
```

```{r input-data}
strict_data <- read.delim(
  source_path,
  stringsAsFactors = FALSE,
  check.names = FALSE,
  quote = "\"",
  comment.char = ""
)

# Inputs average 100 * descending rank / 46704 across ten seeds, with
# average ranks for tied scores. Lower percentiles indicate higher priority.
method_columns <- c(
  "RF" = "RF_motif_percentile",
  "TriNet" = "TriNet_motif_percentile",
  "N2V-MLP" = "N2V_MLP_motif_percentile",
  "TriMoGCL" = "TriMoGCL_motif_percentile",
  "HANAMI" = "HANAMI_motif_percentile"
)
methods <- names(method_columns)

required_columns <- c(
  "candidate_index", "disease_local_id", "disease_mesh_id", "disease_name",
  "drug_local_id", "drugbank_id",
  unname(method_columns)
)
missing_columns <- setdiff(required_columns, names(strict_data))
if (length(missing_columns)) {
  stop(
    "Strict-evidence motif table lacks columns: ",
    paste(missing_columns, collapse = ", ")
  )
}
if (anyNA(strict_data[required_columns])) {
  stop("Strict-evidence motif table contains missing values in required columns")
}
if (anyDuplicated(strict_data$candidate_index)) {
  stop("Each candidate_index must identify exactly one motif")
}

```

## Cohort and significance tests

```{r cohort-analysis}
# Complete clinical evidence cohort.
cohort_disease_ids <- unique(strict_data$disease_mesh_id)
cohort_data <- strict_data
cohort_data$pair_id <- paste(
  cohort_data$disease_mesh_id,
  cohort_data$drugbank_id,
  sep = ":"
)

n_motifs <- nrow(cohort_data)
n_pair_clusters <- length(unique(cohort_data$pair_id))
n_diseases <- length(unique(cohort_data$disease_mesh_id))
stopifnot(n_motifs == 1630L, n_pair_clusters == 785L, n_diseases == 109L)

# Panel b: cohort mean of the ten-seed mean percentile for each motif.
method_means <- vapply(
  method_columns,
  function(column) mean(cohort_data[[column]]),
  numeric(1)
)

# Panel a: unique best-ranked motifs as a percentage of the complete cohort.
motif_percentiles <- as.matrix(cohort_data[unname(method_columns)])
lowest_percentile <- apply(motif_percentiles, 1L, min)
is_best <- motif_percentiles == lowest_percentile
unique_best <- rowSums(is_best) == 1L
n_best_rank_ties <- sum(!unique_best)
best_rank_counts <- colSums(is_best & unique_best)
names(best_rank_counts) <- methods
best_rank_summary <- data.frame(
  method = methods,
  best_ranked_motifs = unname(best_rank_counts[methods]),
  total_motifs = n_motifs,
  percentage = 100 * unname(best_rank_counts[methods]) / n_motifs,
  tied_motifs = n_best_rank_ties,
  stringsAsFactors = FALSE
)
stopifnot(sum(best_rank_counts) + n_best_rank_ties == n_motifs)

# Panels a-b: unadjusted one-sided CR1 t tests, clustered by drug-disease pair.
cluster_robust_t_test <- function(
    differences, panel, endpoint, alternative, baseline,
    hanami_mean, baseline_mean, lower_tail) {
  estimate <- mean(differences)
  residuals <- differences - estimate
  cluster_scores <- rowsum(
    residuals,
    group = cohort_data$pair_id,
    reorder = FALSE
  )[, 1L]

  n <- length(differences)
  clusters <- length(cluster_scores)
  if (clusters < 2L) stop("At least two drug-disease pair clusters are required")

  variance <-
    (clusters / (clusters - 1)) * sum(cluster_scores^2) / (n^2)
  standard_error <- sqrt(variance)
  degrees_freedom <- clusters - 1L
  t_value <- estimate / standard_error
  p_value <- pt(t_value, df = degrees_freedom, lower.tail = lower_tail)
  critical_value <- qt(0.975, df = degrees_freedom)

  data.frame(
    panel = panel,
    endpoint = endpoint,
    test = "One-sided CR1 cluster-robust t test",
    alternative = alternative,
    baseline = baseline,
    diseases = n_diseases,
    pair_clusters = n_pair_clusters,
    motifs = n_motifs,
    hanami_mean = hanami_mean,
    baseline_mean = baseline_mean,
    mean_difference = estimate,
    cluster_robust_se = standard_error,
    ci_low = estimate - critical_value * standard_error,
    ci_high = estimate + critical_value * standard_error,
    df = degrees_freedom,
    t = t_value,
    p_raw = p_value,
    stringsAsFactors = FALSE
  )
}

primary_baseline <- "TriMoGCL"

hanami_unique_best <- as.numeric(
  unique_best & is_best[, match("HANAMI", methods)]
)
trimogcl_unique_best <- as.numeric(
  unique_best & is_best[, match(primary_baseline, methods)]
)
best_share_test <- cluster_robust_t_test(
  differences = hanami_unique_best - trimogcl_unique_best,
  panel = "a",
  endpoint = "Unique-best motif indicator",
  alternative = paste(
    "HANAMI unique-best proportion >", primary_baseline,
    "unique-best proportion"
  ),
  baseline = primary_baseline,
  hanami_mean = mean(hanami_unique_best),
  baseline_mean = mean(trimogcl_unique_best),
  lower_tail = FALSE
)

rank_percentile_differences <-
  cohort_data[[method_columns[["HANAMI"]]]] -
  cohort_data[[method_columns[[primary_baseline]]]]
primary_test <- cluster_robust_t_test(
  differences = rank_percentile_differences,
  panel = "b",
  endpoint = "Mean motif rank percentile",
  alternative = paste(
    "HANAMI mean percentile <", primary_baseline, "mean percentile"
  ),
  baseline = primary_baseline,
  hanami_mean = unname(method_means[["HANAMI"]]),
  baseline_mean = unname(method_means[[primary_baseline]]),
  lower_tail = TRUE
)

clinical_tests <- rbind(best_share_test, primary_test)
clinical_tests$significance <- ifelse(
  clinical_tests$p_raw < 0.001, "***",
  ifelse(
    clinical_tests$p_raw < 0.01, "**",
    ifelse(clinical_tests$p_raw < 0.05, "*", "ns")
  )
)
best_share_test <- clinical_tests[clinical_tests$panel == "a", , drop = FALSE]
primary_test <- clinical_tests[clinical_tests$panel == "b", , drop = FALSE]

dir.create(dirname(output_stats), recursive = TRUE, showWarnings = FALSE)
write.csv(clinical_tests, output_stats, row.names = FALSE)
```

## Prepare the panel data

```{r build-figure-source}
best_share_panel <- data.frame(
  panel = "a",
  panel_type = "best_share",
  panel_title = cohort_label,
  method = methods,
  value = best_rank_summary$percentage,
  bar_order = seq_along(methods),
  comparison_method = "HANAMI",
  reference_method = primary_baseline,
  p_value = best_share_test$p_raw,
  significance = best_share_test$significance,
  stringsAsFactors = FALSE
)

aggregate_panel <- data.frame(
  panel = "b",
  panel_type = "aggregate",
  panel_title = cohort_label,
  method = methods,
  value = unname(method_means[methods]),
  bar_order = seq_along(methods),
  comparison_method = "HANAMI",
  reference_method = primary_baseline,
  p_value = primary_test$p_raw,
  significance = primary_test$significance,
  stringsAsFactors = FALSE
)

# Load the five case-study motifs.
case_data <- read.csv(
  case_source_path,
  stringsAsFactors = FALSE,
  check.names = FALSE
)
required_case_columns <- c(
  "panel", "candidate_index", "motif", "clinical_evidence",
  "clinical_reference"
)
missing_case_columns <- setdiff(required_case_columns, names(case_data))
if (length(missing_case_columns)) {
  stop(
    "Illustrative-case table lacks columns: ",
    paste(missing_case_columns, collapse = ", ")
  )
}

n_cases <- nrow(case_data)
if (n_cases != 5L) stop("The current Figure 5 requires five illustrative cases")
current_case_panels <- letters[seq.int(3L, n_cases + 2L)]
stopifnot(identical(case_data$panel, current_case_panels))
if (anyNA(case_data$candidate_index) || anyDuplicated(case_data$candidate_index)) {
  stop("Illustrative cases must have distinct candidate_index values")
}

case_match <- match(case_data$candidate_index, strict_data$candidate_index)
if (anyNA(case_match)) {
  stop(
    "Illustrative candidate_index values absent from the strict-evidence table: ",
    paste(case_data$candidate_index[is.na(case_match)], collapse = ", ")
  )
}
case_motifs <- strict_data[case_match, , drop = FALSE]
if (any(!case_motifs$disease_mesh_id %in% cohort_disease_ids)) {
  stop("Every illustrative case must belong to the selected disease cohort")
}

if (anyDuplicated(case_motifs$disease_mesh_id)) {
  stop("Each illustrative case must represent a different disease type")
}

case_panels <- cbind(
  case_data[c("panel", "motif")],
  case_motifs[unname(method_columns)]
) %>%
  pivot_longer(
    cols = all_of(unname(method_columns)),
    names_to = "method_column",
    values_to = "value"
  ) %>%
  transmute(
    panel = panel,
    panel_type = "case_study",
    panel_title = motif,
    method = methods[match(method_column, method_columns)],
    value = value,
    bar_order = match(method, methods),
    comparison_method = NA_character_,
    reference_method = NA_character_,
    p_value = NA_real_,
    significance = NA_character_
  ) %>%
  as.data.frame()

source_data <- rbind(best_share_panel, aggregate_panel, case_panels)

# Panels a-b: marginal 95% CR1 confidence intervals conditional on ten-seed means.
cluster_mean_interval <- function(values) {
  estimate <- mean(values)
  scores <- rowsum(values - estimate, cohort_data$pair_id, reorder = FALSE)[, 1L]
  groups <- length(scores)
  standard_error <- sqrt(groups / (groups - 1) * sum(scores^2) / length(values)^2)
  half_width <- qt(0.975, df = groups - 1L) * standard_error
  c(error_lower = estimate - half_width, error_upper = estimate + half_width,
    error_se = standard_error)
}

cohort_errorbars <- do.call(rbind, lapply(seq_along(methods), function(j) {
  winner_interval <- cluster_mean_interval(100 * as.numeric(unique_best & is_best[, j]))
  rank_interval <- cluster_mean_interval(motif_percentiles[, j])
  rbind(
    data.frame(panel = "a", method = methods[j], as.list(winner_interval)),
    data.frame(panel = "b", method = methods[j], as.list(rank_interval))
  )
}))
cohort_errorbars$error_type <- "95% pair-clustered CR1 confidence interval"
cohort_errorbars$error_sd <- NA_real_
cohort_errorbars$error_n <- n_pair_clusters

case_seed_values <- read.csv(seed_source_path, stringsAsFactors = FALSE)
stopifnot(
  all(c("panel", "candidate_index", "method", "seed", "rank_percentile") %in%
        names(case_seed_values)),
  nrow(case_seed_values) == n_cases * length(methods) * 10L,
  !anyDuplicated(case_seed_values[c("panel", "method", "seed")]),
  all(is.finite(case_seed_values$rank_percentile)),
  all(case_seed_values$rank_percentile > 0 & case_seed_values$rank_percentile <= 100),
  identical(sort(unique(case_seed_values$seed)), seq.int(0L, 90L, 10L))
)
# Panels c-g: mean and sample SD across ten seeds.
case_errorbars <- case_seed_values %>%
  group_by(panel, method) %>%
  summarise(
    unique_candidates = n_distinct(candidate_index),
    candidate_index = first(candidate_index),
    seed_mean = mean(rank_percentile),
    error_sd = sd(rank_percentile),
    error_n = n(),
    .groups = "drop"
  )
stopifnot(
  all(case_errorbars$unique_candidates == 1L),
  all(case_errorbars$error_n == 10L),
  all(case_errorbars$candidate_index ==
        case_data$candidate_index[match(case_errorbars$panel, case_data$panel)])
)
case_check <- left_join(case_panels, case_errorbars, by = c("panel", "method"))
stopifnot(!anyNA(case_check$seed_mean), max(abs(case_check$value - case_check$seed_mean)) < 1e-8)

# Panels c-g: exploratory, unadjusted one-sided paired t tests across seeds
# against the baseline with the lowest mean percentile in each panel.
case_tests <- do.call(rbind, lapply(current_case_panels, function(panel_id) {
  panel_means <- case_check[case_check$panel == panel_id, ]
  baselines <- panel_means[panel_means$method != "HANAMI", ]
  baseline <- baselines$method[which.min(baselines$value)]
  values <- case_seed_values[case_seed_values$panel == panel_id, ]
  hanami <- values[values$method == "HANAMI", ]
  comparator <- values[values$method == baseline, ]
  hanami <- hanami[order(hanami$seed), ]
  comparator <- comparator[match(hanami$seed, comparator$seed), ]
  stopifnot(nrow(hanami) == 10L, nrow(comparator) == 10L,
            identical(hanami$seed, comparator$seed),
            identical(hanami$candidate_index, comparator$candidate_index))
  difference <- hanami$rank_percentile - comparator$rank_percentile
  test <- t.test(hanami$rank_percentile, comparator$rank_percentile,
                 paired = TRUE, alternative = "less")
  normality <- shapiro.test(difference)
  # Additional normality and sensitivity diagnostics are exported with the tests.
  sensitivity <- wilcox.test(difference, alternative = "less", exact = TRUE)
  data.frame(
    panel = panel_id, candidate_index = hanami$candidate_index[1L],
    motif = case_data$motif[match(panel_id, case_data$panel)],
    reference_method = "HANAMI", comparison_method = baseline,
    hanami_mean = mean(hanami$rank_percentile),
    baseline_mean = mean(comparator$rank_percentile),
    mean_difference = mean(difference), sd_difference = sd(difference),
    seeds = paste(hanami$seed, collapse = ","), n = length(difference),
    t_statistic = unname(test$statistic), df = unname(test$parameter),
    p_value = test$p.value, shapiro_p = normality$p.value,
    wilcoxon_sensitivity_p = sensitivity$p.value,
    test = "One-sided paired t test across ten matched seeds",
    alternative = "HANAMI mean rank percentile is lower",
    multiplicity_adjustment = "None; exploratory comparisons",
    stringsAsFactors = FALSE
  )
}))
dir.create(dirname(output_case_tests), recursive = TRUE, showWarnings = FALSE)
write.csv(case_tests, output_case_tests, row.names = FALSE)
for (i in seq_len(nrow(case_tests))) {
  selected <- source_data$panel == case_tests$panel[i]
  source_data$comparison_method[selected] <- case_tests$comparison_method[i]
  source_data$reference_method[selected] <- "HANAMI"
  source_data$p_value[selected] <- case_tests$p_value[i]
  source_data$significance[selected] <- if (case_tests$p_value[i] < 0.001) {
    "***"
  } else if (case_tests$p_value[i] < 0.01) {
    "**"
  } else if (case_tests$p_value[i] < 0.05) {
    "*"
  } else "ns"
}
case_errorbars <- case_errorbars %>%
  transmute(
    panel, method,
    error_lower = seed_mean - error_sd,
    error_upper = seed_mean + error_sd,
    error_se = NA_real_,
    error_type = "Sample SD across ten seeds",
    error_sd, error_n
  )
source_data <- left_join(
  source_data, bind_rows(cohort_errorbars, case_errorbars),
  by = c("panel", "method")
)
stopifnot(
  all(is.finite(source_data$error_lower)), all(is.finite(source_data$error_upper)),
  all(source_data$error_lower <= source_data$value),
  all(source_data$error_upper >= source_data$value)
)
expected_panel_order <- letters[seq_len(n_cases + 2L)]
stopifnot(
  identical(unique(source_data$panel), expected_panel_order),
  all(table(source_data$panel) == length(methods)),
  all(is.finite(source_data$value)),
  all(is.finite(source_data$p_value)),
  all(source_data$p_value >= 0 & source_data$p_value <= 1)
)
dir.create(dirname(output_source), recursive = TRUE, showWarnings = FALSE)
write.csv(source_data, output_source, row.names = FALSE)

case_summary <- cbind(case_data, case_motifs[unname(method_columns)])
write.csv(
  case_summary,
  output_case_summary,
  row.names = FALSE
)

# Prepare the long-format plotting table.
df_long <- source_data %>%
  rename(Model = method, Metric = panel_title, Score = value)
df_long$Model <- factor(df_long$Model, levels = methods)
```

## Create individual panels

```{r plotting-functions}
method_colors_clinical <- c(
  "RF" = "#2C8C99",
  "TriNet" = "#E1A6AD",
  "N2V-MLP" = "#92B1B6",
  "TriMoGCL" = "#CAD0BD",
  "HANAMI" = "#E28B62"
)

format_title <- function(title, panel_type) {
  if (panel_type != "case_study") return(title)
  sub("^([^-]+-[^-]+)-", paste0("\\1-", "\n"), title)
}

five_tick_breaks <- function(content_max) {
  step <- ceiling((content_max / 4) / 5) * 5
  if (!is.finite(step) || step <= 0) step <- 5
  # Five equally spaced labels, never above the percentile bound of 100.
  # Plot limits are set separately so the full SD intervals remain visible.
  min(step, 25) * 0:4
}

create_single_panel_clinical <- function(data, motif_title, colors) {
  data <- data[order(data$bar_order), , drop = FALSE]
  panel_type <- data$panel_type[[1]]
  panel_letter <- data$panel[[1]]
  panel_index <- match(panel_letter, letters)
  panel_column <- ((panel_index - 1L) %% layout_columns) + 1L
  panel_row <- ceiling(panel_index / layout_columns)
  # Panel frame and axis layout.
  y_title_right_margin <- 4.4
  y_title_vjust <- if (panel_column == 1L) 0.5 else 0.25
  panel_tag_x <- -0.1311
  plot_left_margin <- if (panel_column == 1L) 29 else 3
  plot_right_margin <- if (panel_column < layout_columns) 3 else 5
  # Reallocate outer whitespace to the space between the two panel rows.
  plot_top_margin <- if (panel_row == 1L) 10 else 22
  plot_bottom_margin <- if (panel_row == 1L) 18 else 6

  custom_theme <- theme_bw(base_size = 14) +
    theme(
      plot.tag = element_text(colour = "black", face = "bold", size = 22),
      plot.tag.location = "panel",
      plot.title = element_text(
        colour = NA, face = "plain", hjust = 0.5, lineheight = 0.95,
        margin = margin(b = 10)
      ),
      axis.title.x = element_blank(),
      axis.title.y = element_text(
        size = 18, face = "plain", vjust = y_title_vjust,
        margin = margin(r = y_title_right_margin)
      ),
      axis.text.x = element_blank(),
      axis.ticks.x = element_blank(),
      axis.text.y = element_text(size = 16, colour = "black"),
      axis.line = element_blank(),
      axis.line.x = element_blank(),
      axis.line.y = element_blank(),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      panel.background = element_rect(fill = "white", colour = NA),
      plot.background = element_rect(fill = "white", colour = NA),
      panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.5),
      legend.position = "none",
      plot.margin = margin(
        plot_top_margin, plot_right_margin,
        plot_bottom_margin, plot_left_margin
      ),
      aspect.ratio = 1
    )

  # Use the same method order in each panel.
  stopifnot(identical(as.character(data$Model), methods))
  data$x_position <- seq_along(methods)
  title <- format_title(motif_title, panel_type)

  significance_values <- unique(data$significance[
    !is.na(data$significance) & data$significance != "ns"
  ])
  has_significance <- length(significance_values) == 1L
  if (length(significance_values) > 1L) {
    stop("A panel may contain at most one displayed significance comparison")
  }
  case_pvalues <- unique(data$p_value[is.finite(data$p_value)])
  has_case_pvalue <- panel_type == "case_study" && length(case_pvalues) == 1L
  has_annotation <- has_significance || has_case_pvalue
  annotation_label <- if (has_case_pvalue) {
    if (has_significance) significance_values[[1L]] else "n.s."
  } else if (has_significance) significance_values[[1L]] else ""

  base_max <- max(data$Score, 1)
  interval_max <- max(data$error_upper, 1)
  # Position mean labels above the full error bars.
  label_gap <- interval_max * 0.025
  data$label_y <- data$error_upper + label_gap
  ymin <- if (min(data$error_lower) < 0) min(data$error_lower) - interval_max * 0.025 else 0
  label_extent <- max(data$label_y) + label_gap
  y_breaks <- five_tick_breaks(label_extent)
  annotation_y <- NA_real_
  if (has_annotation) {
    comparison <- data$comparison_method[[1]]
    reference <- data$reference_method[[1]]
    compared <- data$error_upper[data$Model %in% c(comparison, reference)]
    if (has_case_pvalue) {
      positions <- sort(match(c(comparison, reference), methods))
      compared <- data$error_upper[seq.int(positions[1L], positions[2L])]
    }
    annotation_y <- max(compared) + interval_max * 0.12
    ymax <- max(max(y_breaks) + interval_max * 0.06,
                label_extent + interval_max * 0.06,
                annotation_y + interval_max * 0.08)
  } else {
    ymax <- max(max(y_breaks), label_extent) * 1.05
  }

  y_label_text <- if (panel_type == "best_share") {
    "Motifs ranked best (%)"
  } else if (panel_type == "aggregate") {
    "Rank percentile (%)"
  } else {
    "Rank percentile (%)"
  }

  data$value_label <- if (panel_type == "best_share") {
    sprintf("%.2f", data$Score)
  } else {
    sprintf("%.2f", data$Score)
  }

  p <- ggplot(data, aes(x = x_position, y = Score, fill = Model)) +
    geom_col(colour = "black", width = 0.68, linewidth = 0.5) +
    geom_errorbar(
      aes(ymin = error_lower, ymax = error_upper),
      width = 0.20, linewidth = 0.5, colour = "black", show.legend = FALSE
    ) +
    geom_text(aes(y = label_y, label = value_label), vjust = 0, size = 11 / ggplot2::.pt) +
    annotation_custom(
      grob = grid::textGrob(
        label = title,
        x = grid::unit(0.5, "npc"),
        y = grid::unit(1.111, "npc"),
        gp = grid::gpar(
          fontsize = 15.5, fontface = "plain", col = "black",
          lineheight = 0.85
        )
      ),
      xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf
    ) +
    scale_fill_manual(values = scales::alpha(colors, bar_alpha)) +
    scale_x_continuous(
      limits = c(0.4, 5.6),
      breaks = data$x_position,
      labels = as.character(data$Model),
      expand = expansion(mult = 0)
    ) +
    scale_y_continuous(
      limits = c(ymin, ymax),
      breaks = y_breaks,
      expand = expansion(mult = c(0, 0.02))
    ) +
    coord_cartesian(clip = "off") +
    labs(tag = panel_letter, title = " ", x = NULL, y = y_label_text) +
    custom_theme +
    theme(plot.tag.position = c(panel_tag_x, 1.12))

  # Display red stars or black n.s. for the selected comparison.
  if (has_annotation) {
    x1 <- match(data$comparison_method[[1]], methods)
    x2 <- match(data$reference_method[[1]], methods)
    if (is.na(x1) || is.na(x2)) {
      stop("Significance comparison methods are absent from panel")
    }
    tick <- ymax * 0.02
    p <- p +
      annotate(
        "segment", x = x1, xend = x2,
        y = annotation_y, yend = annotation_y,
        colour = "black", linewidth = 0.5
      ) +
      annotate(
        "segment", x = x1, xend = x1,
        y = annotation_y, yend = annotation_y - tick,
        colour = "black", linewidth = 0.5
      ) +
      annotate(
        "segment", x = x2, xend = x2,
        y = annotation_y, yend = annotation_y - tick,
        colour = "black", linewidth = 0.5
      ) +
      annotate(
        "text", x = (x1 + x2) / 2,
        y = annotation_y + ymax * if (has_significance) 0.005 else 0.025,
        label = annotation_label,
        colour = if (has_significance) "red" else "black",
        fontface = "plain", size = if (has_significance) 7 else 14 / ggplot2::.pt,
        vjust = if (has_significance) 0.25 else 0
      )
  }

  return(p)
}
```

## Assemble and save Figure 5

```{r assemble-and-save, fig.width=params$width, fig.height=params$height}
level_order <- unique(df_long$panel)
plots_clinical <- list()
for (i in seq_along(level_order)) {
  panel_data <- subset(df_long, panel == level_order[i])
  plots_clinical[[i]] <- create_single_panel_clinical(
    panel_data, panel_data$Metric[[1]],
    method_colors_clinical
  )
}

caption_parts <- character(0)
if (n_best_rank_ties > 0L) {
  caption_parts <- c(
    caption_parts,
    sprintf("Panel a excludes %d tied winners from the numerators.", n_best_rank_ties)
  )
}
caption_text <- if (length(caption_parts)) {
  paste(caption_parts, collapse = "\n")
} else {
  NULL
}

# Append the legend after the seven panels, in a four-column, two-row layout.
plots_clinical[[length(plots_clinical) + 1L]] <- guide_area()
plots_with_legend <- lapply(plots_clinical, function(p) {
  p + theme(legend.position = "right")
})

final_design_clinical <- wrap_plots(plots_with_legend, ncol = layout_columns) +
  plot_layout(guides = "collect") +
  plot_annotation(
    caption = caption_text,
    theme = theme(
      plot.caption = element_text(size = 8, hjust = 0)
    )
  ) &
  theme(
    legend.title = element_blank(),
    legend.text = element_text(size = 18, face = "plain"),
    legend.key.size = grid::unit(1.2, "cm"),
    legend.box.margin = margin(l = 20)
  )

print(final_design_clinical)

dir.create(dirname(output_pdf), recursive = TRUE, showWarnings = FALSE)
dir.create(dirname(output_png), recursive = TRUE, showWarnings = FALSE)
ggsave(output_pdf, plot = final_design_clinical, width = params$width, height = params$height)
ggsave(
  output_png,
  plot = final_design_clinical,
  width = params$width,
  height = params$height,
  dpi = params$dpi,
  bg = "white"
)

print(paste("Plot saved successfully to:", output_pdf))
```
